---
title: "WHO_website"
author: "Emma"
date: "17/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(httr)
library(tidyverse)
library(curl)
```

## R Markdown

We are going to bulk download report

```{r cars}
covid_reports <- 'https://www.who.int/emergencies/diseases/novel-coronavirus-2019/situation-reports'
```


Check that is is Ok to scrape website


Start with one report

```{r}

page_report_link <- 'https://www.who.int/publications/m/item/weekly-epidemiological-update-on-covid-19---31-august-2021'
page_report <- page_report_link %>% 
  bow() %>% 
  scrape()
url <- page_report %>% 
  html_elements(".button-blue-background") %>% 
  html_children() %>% 
  html_attr('href')

```


Download report

```{r}

curl_download(url, destfile = here::here('temp.pdf'))

```

Now that it works for one page we are going to get the links to all the report landing pages. 




```{r}

page <- covid_reports %>% 
  bow() %>% 
  scrape()
list_of_pages <- page %>% 
  html_elements(".sf-list-vertical__item") %>% 
  html_attr('href') 


page %>% 
  html_elements(".sf-list-vertical__item") %>% 
  html_attr('href')

```
We have the URLs we need

Before we mass download we are going to get a better name for the files.
```{r}
page_report %>% 
  html_elements('.dynamic-content__heading') %>% 
  html_text()
```
It is good practice to test your code on a small subset of your problem. 

```{r}
# create small version of the list
list_of_pages_mini <- list_of_pages[1:3]
```

We are going to use two functions from the `purrr` package to iterate over items in our list. 

```{r}
?map
```


```{r}


report_download_url <- map(list_of_pages_mini, ~read_html(.x) %>% 
      html_elements(".button-blue-background") %>% 
      html_children() %>% 
      html_attr('href'))



report_names <- map(list_of_pages_mini, ~read_html(.x) %>% 
                      html_elements('.dynamic-content__heading') %>% 
                      html_text())
map2(report_download_url, report_names, 
     ~curl_download(.x, paste(.y, '.pdf')))
```

